---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MaximinInfer

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/MaximinInfer)](https://CRAN.R-project.org/package=MaximinInfer)
<!-- badges: end -->

MaximinInfer is a package that implements the sampling and aggregation method for the covariate-shift Maximin effect, which was proposed in <arXiv:2011.07568>. It constructs the confidence interval for any linear combination of the high-dimensional Maximin effect.

## Installation

You can install the released version of MaximinInfer from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("MaximinInfer")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zywang0701/MaximinInfer")
```
## Example

This is a basic example which shows you how to solve a common problem:
```{r package, message=FALSE}
library(MaximinInfer)
```

The data is heterogeneous and covariates shift between source and target data
```{r}
## number of groups
L=2
## dimension
p=100

## mean vector for source
mean.source = rep(0, p)
## covariance matrix for source
A1gen <- function(rho,p){
  A1=matrix(0,p,p)
  for(i in 1:p){
    for(j in 1:p){
      A1[i,j]<-rho^(abs(i-j))
    }
  }
  return(A1)
}
cov.source = A1gen(0.6, p)

## 1st group's source data
n1 = 100
X1 = MASS::mvrnorm(n1, mu=mean.source, Sigma=cov.source)
# true coef for 1st group
b1 = rep(0, p)
b1[1:5] = seq(1,5)/20
b1[98:100] = c(0.5, -0.5, -0.5)
Y1 = X1%*%b1 + rnorm(n1)

## 2nd group's source data
n2 = 100
X2 = MASS::mvrnorm(n2, mu=mean.source, Sigma=cov.source)
# true coef for 2nd group
b2 = rep(0, p)
b2[6:10] = seq(1,5)/20
b2[98:100] = 0.5*c(0.5, -0.5, -0.5)
Y2 = X2%*%b2 + rnorm(n2)

## Target Data, covariate shift
n0 = 100
mean0 = rep(0, p)
cov0 = cov.source
for(i in 1:p) cov0[i, i] = 1.5
for(i in 1:5) for(j in 1:5) if(i!=j) cov0[i, j] = 0.9
for(i in 99:100) for(j in 99:100) if(i!=j) cov0[i, j] = 0.9
X0 = MASS::mvrnorm(n0, mu=mean0, Sigma=cov0)
```

Input the loading. Note that it allows for multiple loading simultaneously.
```{r}
loading.mat = matrix(0, nrow=100, ncol=2) # dimension p=100
loading.mat[96:100, 1] = 0.4
loading.mat[99:100, 2] = 0.8
```

Call function `Maximin()`. By setting the argument verbose, you can choose whether or not to display the intermediate bias-correction results.
```{r}
mm <- Maximin(list(X1,X2), list(Y1,Y2), loading.mat, X0, cov.shift=TRUE, verbose=TRUE)
```

The following inference method is:
```{r}
out <- Infer(mm, gen.size=200)
```

The weights for each group:
```{r}
out$weight
```

The point estimator and its corresponding confidence interval for each loading:
```{r}
out$mminfer
```

